BOLD Parameter Estimation Using Particle Filters

### 2010-09-02 doc/thesis/background.tex
just need to edit discussion/conclusion, change captions and copy some graphs from defense

\begin{figure}
\includegraphics[width=16cm]{images/kalman}
%\includegraphics[trim=6cm .75cm 6cm .75cm,width=16cm]{images/gauss_step_point1sec_3sigma.pdf}
\caption{Example updates of a distribution using the Kalman Filter.}
\label{fig:EKFWorking}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[trim=6cm .75cm 6cm .75cm,width=16cm]{images/gauss_step_point1sec_3sigma.pdf}
\caption{Distributions of state variables after simulating for $0.1$s}
\label{fig:transp1s}
\end{figure}

\begin{figure}
\includegraphics[trim=6cm .75cm 6cm .75cm,width=16cm]{images/gauss_step_1sec_3sigma.pdf}
\caption{Distributions of state variables after simulating for $1$s}
\label{fig:trans1s}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=16cm]{images/kalman2}
\caption[Example Kalman Filter Progression]
{a) Sigma Points are passed through the state/measurement equations
to get a state prediction (green line). The first two moments of
the state prediction are then used to estimate the distribution with
a Gaussian (red line). The distribution centered at the new measurement,
estimating measurement error (dark blue), is then combined with the existing
state prediction (red line) to get the new estimated state (light blue).
The same process is applied in b), and c) with different measurements and
initial state estimates.}
\label{fig:EKFWorking}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[trim=6cm .75cm 6cm .75cm,width=16cm]{images/gauss_step_point1sec_3sigma.pdf}
\caption[Q-Q Plot Of Standard Normal and Result of $0.1$s BOLD Simulation Output]
{Q-Q Plot Of Standard Normal and Result of $0.1$ BOLD Simulation Output. A
perfect Gaussian would fall on the green line}
\label{fig:transp1s}
\end{figure}

\begin{figure}
\includegraphics[trim=6cm .75cm 6cm .75cm,width=16cm]{images/gauss_step_1sec_3sigma.pdf}
\caption{Q-Q Plot Of Standard Normal and Result of $1$s BOLD Simulation Output}
\label{fig:trans1s}
\end{figure}
